Exploring the Validity Range of PLL Analytical Models

### 2025-05-08 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Fixing repots.

Hence, the maximum input frequency step that still allows theoretical predictability is `{python} format(step_m_lin)` Hz. If the input frequency step exceeds this limit, the PLL may lose lock and exhibit cycle slipping.

@@

>>>>

Hence, the maximum input frequency step that still allows theoretical predictability is `{python} format(step_m_lin)`Hz. If the input frequency step exceeds this limit, the PLL may lose lock and exhibit cycle slipping (more details are provided in the next section).

@@

# Cycle Slipping

Cycle slipping is an undesired phenomenon in Phase-Locked Loops (PLLs) that occurs when the phase error between the reference input and the feedback output exceeds the linear range of the system.

Cycle slipping occurs when the PLL is unable to maintain phase lock, and the phase error grows beyond $2\pi$, resulting in a temporary loss of synchronization. The loop then slips by one or more full cycles before attempting to reacquire lock.
